Sexual selection and extinction: a macro-evolutionary approach

### 2018-06-27 Sexual Selection and Extinction.Rmd

It is likely that given the underestimation of rate shifts by BAMM we obtain groups of similar speciation/extinction rates and thus when used in PGLS the highly correlated species will have near exact extinction/speciation rates. Giving less weight to these results.

>>>>

> My gut feeling: It is likely that given the underestimation of rate shifts by BAMM we obtain groups of similar speciation/extinction rates and thus when used in PGLS the highly correlated species will have near exact extinction/speciation rates. Giving less weight to these results.
